Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
figure order

\begin{definition}
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$.
See \fref{fig:kissingCrossing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
\end{definition}

\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=1]{kissingCrossing}}
	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right). For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
	\label{fig:kissingCrossing}
\end{figure}

@@

\begin{remark}
A quick disclaimer about accordion complexes and slalom complexes of arbitrary dissections.
As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
This prevents to use the definitions given in this section.
Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
\vincent{A retravailler}
\end{remark}

@@

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{orderCurves}}
	\caption{The order~$\prec_\alpha$ is given by the order in which the curves cross the angle corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

>>>>

\begin{definition}
\label{def:kiss}
Let~$\omega,\omega' \in \walks^\pm(\bar Q)$ be two undirected walks on~$\bar Q$.
We say that~$\omega$ \defn{kisses}~$\omega'$ if~$\Sigma_\top(\omega) \cap \Sigma_\bottom(\omega') \ne \varnothing$.
See \fref{fig:kissing}.
% \ie if there exist a common substring~$\sigma \in \strings^\pm(\bar Q)$ of~$\omega$ and~$\omega'$ such that the arrows of~$\omega$ incident to~$\sigma$ are both outgoing while the arrows of~$\omega'$ incident to~$\sigma$ are both incoming.
We say that~$\omega$ and~$\omega'$ are \defn{kissing} if~$\omega$ kisses~$\omega'$ or~$\omega'$ kisses~$\omega$ (or both).
Note that we authorize the situation where~$\sigma$ is reduced to a vertex~$v$, meaning that~$v$ is a peak of~$\omega$ and a deep of~$\omega'$.
Observe also that~$\omega$ can kiss~$\omega'$ several times, that~$\omega$ and~$\omega'$ can mutually kiss, and that~$\omega$ can kiss itself.
We denote by~$\NKWalks(\bar Q)$ the walks on~$\bar Q$ which are not self-kissing and by~$\NKWalks^\pm(\bar Q) \eqdef \set{\{\omega, \omega^{-1}\}}{\omega \in \NKWalks(\bar Q)}$ their undirected version.
\end{definition}

\begin{figure}
	\capstart
	\centerline{\includegraphics[scale=1]{kissing}}
	\caption{A schematic representation of two kissing walks: $\omega$~kisses~$\omega'$.}
	\label{fig:kissing}
\end{figure}

@@

\begin{remark}
A quick disclaimer about accordion complexes and slalom complexes of arbitrary cellular dissections.
As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual cellular dissection~$\dissection\dual$.
This prevents to use the definitions given in this section.
Although its accordion complex (resp.~slalom complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~slalom complexes) defined in this paper.
See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
\end{remark}

@@

\begin{remark}
\label{rema:countercurrentOrderOnSurface}
Using Theorem \ref{thm:complexesCoincide}, we can translate the definition of the countercurrent order~$\prec_\alpha$ to the language of~$\dissection$-accordions.
An arrow~$\alpha$ in~$\bar Q\blossom$ corresponds to an angle at a point $v$ between two arcs of~$\dissection$.
Two distinct non-kissing walks~$\mu_\star, \nu_\star$ marked at~$\alpha$ in~$\bar Q$ correspond to two distinct non-crossing~$\dissection$-accordions~$\gamma$ and~$\delta$ passing in front of this angle.
Then~$\gamma \prec_\alpha \delta$ if~$\gamma$ passes closer to~$v$ than~$\delta$ does.
\pierreguy{Should we prove this?}
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{orderCurves}}
	\caption{The order~$\prec_\alpha$ on marked walks is the order in which the corresponding curves cross the angle corresponding to~$\alpha$.}
	\label{fig:orderCurves}
\end{figure}
\end{remark}

%\begin{figure}
%	\capstart
%	\centerline{\includegraphics[scale=1]{kissing}}
%	\caption{A schematic representation of two kissing walks (left) and two crossing walks~(right): $\omega$~kisses~$\omega'$ (left) while~$\mu$~crosses~$\nu$ (right). For the crossing walks, we have~$\mu \prec_\gamma \nu$ while~$\nu \prec_\delta \mu$.}
%	\label{fig:kissing}
%\end{figure}
